%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {SSI (Safety Service and Inspection L.L.C)}      % Organization
    {Robotics Engineer} % Job title
    {Jul. 2017 - PRESENT} % Date(s)
    {Tulsa,OK} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Achieve autonomous navigation of UAVs using NVidia Jetson TK1 as the Onboard Embedded System, which is a part of developing automation solutions for surveyors to use industrial drones for precise data collection.}
        \item {Implement autonomous motion planning with custom sensor fusion and control packages written for Linux/ROS in C++ and Python.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Oklahoma State University} % Organization
    {Graduate Teaching Assistant} % Job title
    {Jan. 2015 - May. 2017} % Date(s)
    {Stillwater, OK} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed design specifications using both basic and advanced part modeling features, Assembly Modeling, Drawings, Sheet Metal, Weldments, and Surfacing in SolidWorks.}
        \item {Performed Motion Analysis and FEA for the parts and Assemblies developed.}
        \item {Administered 3D printing and CNC Machine Shop utilizing CNC lathes, Mills, and Turning Centers.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Jawaharlal Nehru Technological University} % Organization
    {Research Assistant} % Job title
    {Jan. 2014 - Jun. 2014} % Date(s)
    {Telangana, INDIA} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and fabricated a Micro-Air Vehicle based on a Tricopter platform and demonstrated at an International conference.}
        \item {Coached Undergraduate students in understanding the dynamics and controls involved in Multi-rotors.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
