%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cvprojectentry
    {Sample Search and Return – Mars Rover} % Project title
    {May 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Programmed a computer vision pipeline (using Python and OpenCV) to perform color thresholding, perspective and coordinate transforms to complete the task of autonomous mapping and navigation of a rover in a simulated Unity environment.}
        \item {Accomplished the task of collecting samples with highest fidelity by adding a robust decision making hierarchy.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cvprojectentry
    {Optimal Trajectory Planning using Multi-objective optimization for Sawyer robot} % Project title
    {Jan 2017 – May 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Proposed trajectory optimization for a 7-DOF sawyer robotic manipulator using NSGA – 2 (Non-dominated Sorting Genetic Algorithm).}
        \item {Implemented the algorithm and controlled the manipulator using ROS and Python. Generated optimal trajectories by performing simulations in Moveit!, considering Joint space and Cartesian space travel, Joint torques and Obstacle avoidance as objectives.}
        \item {Achieved significant decrease in the considered objectives over OMPL (Open Motion Planning Library - PRM and RRTs).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cvprojectentry
    {Real-Time Obstacle Avoidance for Manipulators and Mobile Robots} % 
    {Aug 2016 – Dec 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Formulated a MATLAB Simulation of real-time obstacle avoidance for a 2-Link planar manipulator.}
        \item {Planned collision-free trajectories using artificial potential fields in the workspace and controlled the motion of the manipulator by defining operational space.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cvprojectentry
    {Hardware in the loop Simulation of an Autonomous Golf Cart} % Job title
    {Aug 2014 – Dec 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Formulated hardware in the loop simulations for an Autonomous Golf cart in V-Rep.}
        \item {Modeled sensors (SONARS and LIDARS) for Simultaneous Localization \& Mapping (SLAM), and actuators for velocity control.}
        \item {Developed Dynamic RRT algorithm for path planning in C++ and validated the optimal path achieved against RRT and A*.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
